## Explotary Data Analysis (EDA) with R ##
 
### Introduction ###
First we will install tidyverse package and load it into our R session.
Then we will load the dataset into our R session.
other Packaegs that i Will use are skimr, summary Tools 
```{r}
install.packages("tidyverse")
library(tidyverse)
install.packages("skimr")
library(skimr)
install.packages("summarytools")
library(summarytools)
```

**Import the dataset**
```{r}
data <- read.csv("sepsis.csv")
```

show data structure
```{r}
str(data)
```
show column names
```{r}
colnames(data)
```
show first 6 rows
```{r}
head(data)
```
show last 6 rows
```{r}
tail(data)
```
show summary of the data
```{r}
summary(data)
```
show the data in a table format
```{r}
View(data)
```

show tibble
```{r}
tibble(data)
```
gimpse of the data
```{r}
glimpse(data)
```
skim the data
```{r}
skim(data)
```
Error in skim(data) : could not find function "skim"
```{r}
dfSummary(data)
```
freq(): This function generates frequency tables for categorical variables, including counts, percentages, and cumulative percentages.
```{r}
freq(data)
```

### import data visualization packages ###
```{r}
install.packages("ggplot2")
library(ggplot2)
install.packages("visdat")
library(visdat)
#install fun modelling
install.packages("funModeling")
library(funModeling)
```

show data with vizdat
```{r}
vis_dat(data)
```
see missing values
```{r}
vis_miss(data)
```
select numeric columns from data to see corrlations
```{r}
data_num <- data %>% select_if(is.numeric)

```
```{r}
vis_cor(data_num)
```
select only numberic columns that are required for the analysis
```{r}
data_num <- data %>% select(5,6,7,8)
```
vusialize the data corrlations
```{r}
vis_cor(data_num)
```
two functions of funModeling package
```{r}
freq(data)
```

plot_num to plot histogram of numeric values

```{r}
plot_num(data)
```
now we will look into dlooker package
```{r}
install.packages("dlookr")
library(dlookr)
```
```{r}










